Rapid Georectification of Pushbroom Hyperspectral Imagery for Real Time Processing by an Autonomous Aerial Vehicle

### 2023-09-11 paper/paper.tex
Updates from Overleaf

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=10.5cm]{./figures/annotated-hsi.eps}
    \caption{Radiance spectrum captured for single HSI pixel.}
    \label{fig:pipeline}
\end{figure}

@@

@@

\begin{table}[H]
\caption{Resampling times as a function of pixel resolution.\label{tab1}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CC}
\toprule
\textbf{Resolution (m)}	& \textbf{Execution time (s)}\\
\midrule
0.5		&   1.328	\\
0.25    &   1.547	\\
0.1     &   3.557   \\
0.05    &   9.235   \\
\bottomrule
\end{tabularx}
\end{table}

\begin{table}[H]
  \caption{Loading and Reflectance Conversion Times.\label{tab1}}
  \newcolumntype{C}{>{\centering\arraybackslash}X}
  \begin{tabularx}{\textwidth}{CC}
    \toprule
    \textbf{Number of scan lines}	& \textbf{Execution time (s)}\\
    \midrule
    371		&   2.049	\\
    725    &   4.219	\\
    1000     &   5.875   \\
    \bottomrule
  \end{tabularx}
\end{table}

>>>>

\subsection{Drone Components}

\begin{figure}[H]
    \centering
    \includegraphics[width=12cm]{./assets/annotated-drone.eps}
    \caption{Components of the Autonomous Drone HSI platform.}
    \label{fig:drone-components}
\end{figure}

@@

@@

\begin{figure}[H]
    \begin{adjustwidth}{-\extralength}{0cm}
        \centering
        \includegraphics[width=15.5cm]{./figures/hsi-infographic.eps}
    \end{adjustwidth}
    \caption{Annotated view of a hyperspectral data cube showcasing sampled spectra for a variety of constituents.\label{fig:hsi-infographic}}
\end{figure}

@@

\begin{table}[H]
\caption{Resampling times as a function of pixel resolution.\label{tab1}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CC}
\toprule
\textbf{Resolution (m)}	& \textbf{Execution time (s)}\\
\midrule
0.5		&   1.434	\\
0.4     &   1.545	\\
0.3     &   1.673   \\
0.2     &   1.802   \\
0.1     &   4.026   \\
0.05    &   10.537  \\ 
\bottomrule
\end{tabularx}
\end{table}

\begin{table}[H]
  \caption{Loading and Reflectance Conversion Times.\label{tab1}}
  \newcolumntype{C}{>{\centering\arraybackslash}X}
  \begin{tabularx}{\textwidth}{CC}
    \toprule
    \textbf{Number of scan lines}	& \textbf{Execution time (s)}\\
    \midrule
    371		&   2.060	\\
    725     &   4.227	\\
    1000    &   5.901   \\
    \bottomrule
  \end{tabularx}
\end{table}
